A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing

### 2019-08-30 1_intro.tex
Small changes by Jun and Tim

\begin{figure}\centering
\includegraphics[width=\columnwidth]{sources-intro-TEST-naive-accuracy.png}
\includegraphics[width=\columnwidth]{sources-intro-TEST-Center-widths.png}
\includegraphics[width=\columnwidth]{sources-intro-TEST-InwardDistributed-widths.png}
\caption{
Toolpaths for a wedge shape using the uniform offsetting approach (top), the approach by \citeauthor{Jin2017JMS}(middle) and our approach (bottom).
Overfill in orange, underfill in azure, narrow beads in blue and wide beads in red.
The wedge shape can be read like a graph plot: for each model diameter we can read out the resulting over- or underfill if a model has thin features with that particular diameter.
}
\label{intro_wedge}
\end{figure}

>>>>

\begin{figure}\centering
\includegraphics[width=\columnwidth]{sources/intro/TEST_naive_accuracy.png}
\includegraphics[width=\columnwidth]{sources/intro/TEST_Center_widths.png}
\includegraphics[width=\columnwidth]{sources/intro/TEST_InwardDistributed_widths.png}
\caption{
Toolpaths for a wedge shape using the uniform offsetting approach (top), the approach by \citeauthor{Jin2017JMS}(middle) and our approach (bottom).
Overfill in orange, underfill in azure, narrow beads in blue and wide beads in red.
The wedge shape can be read like a graph plot: for each model diameter we can read out the resulting over- or underfill if a model has thin features with that particular diameter.
}
\label{intro_wedge}
\end{figure}
